---
title: "Google Play Store Data Analysis"
author: "Anthony Le"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE}
#install.packages("tidyverse")
#install.packages("randomForest")
#install.packages('caret', dependencies = TRUE)
#install.packages('e1071')
#install.packages('DMwR')
library(DMwR)
library(e1071)
library(caret)
library(randomForest)
library(tidyverse)
library(lubridate)
set.seed(1958)
```

## Data Import

Import Data 
```{r}
playstore <- read.csv('googleplaystore.csv', header = TRUE)
```


Initial Data
```{r,echo=FALSE}
str(playstore)
summary(playstore)

```

## Transform Data

1. Remove columns and duplicated rows

```{r, echo=FALSE}
playstore$App <- NULL
playstore$Current.Ver <- NULL
playstore$Genres <- NULL
playstore$Last.Updated <- NULL
playstore <- na.omit(playstore)
playstore <- subset(unique(playstore))

```
2. App ratings should have a maximum value of 5

```{r, echo=FALSE}
playstore <- subset(playstore[playstore$Rating <= 5,])

```


3. Remove extra characters, convert Size to consistent format, remove apps under 1MB, and remove apps with 0 installs

```{r,echo=FALSE}
playstore$Installs <- gsub("+", "", playstore$Installs, fixed = TRUE)
playstore$Installs <- gsub(",", "", playstore$Installs, fixed = TRUE)
playstore$Price <- gsub("$", "", playstore$Price, fixed = TRUE)
playstore$Price <- gsub("0", "0.00", playstore$Price, fixed = TRUE)
playstore <- subset(playstore[playstore$Size != "Varies with device",])

playstore <- playstore[!grepl("k",playstore$Size),]
playstore$Size <- gsub("M", "", playstore$Size)
playstore$Size <- gsub(",", "", playstore$Size, fixed = TRUE)
playstore$Size <- as.numeric(playstore$Size)
playstore <- as.vector(na.omit(playstore))


```


4. Convert columns to appropriate variable types

```{r, echo=FALSE}

# Android.Ver should have numeric values only
playstore$Android.Ver <- gsub("and up","",playstore$Android.Ver,fixed=TRUE)
playstore$Android.Ver <- gsub("Varies with device",NA,playstore$Android.Ver)
playstore <- as.vector(na.omit(playstore))
playstore$Android.Ver <- substr(playstore$Android.Ver,start=1,stop=3)

# Change data type of  Reviews, Rating, Price, Installs
playstore$Reviews <- as.numeric(playstore$Reviews)
playstore$Rating <- as.numeric(playstore$Rating)
playstore$Price <- as.numeric(playstore$Price)
playstore$Installs <- as.numeric(playstore$Installs)
playstore$Category <- factor(playstore$Category)

# Remove NaN values in Type
playstore$Type <- gsub(NaN,NA,playstore$Type,fixed=TRUE)
playstore$Type <- factor(playstore$Type)
playstore$Android.Ver <- gsub(NaN,NA,playstore$Android.Ver,fixed=TRUE)
playstore$Android.Ver <- factor(playstore$Android.Ver)


playstore <- na.omit(playstore)
str(playstore)
```


```{r, echo=FALSE}
hist(playstore$Rating, main = "Distribution of App Rating, Continuous", breaks = 100, xlim = c(0,5), xlab = "Rating", ylab = "Count", col="gold")

```

There is a clear class imbalance, as there are far more apps rated 4.0 and above

## Create Ratings Intervals

Split continuous rating (1.0-5.0) into 2 intervals and convert to factor
```{r}
playstore$Rating <- cut(as.numeric(playstore$Rating), breaks = c(1,4,5), labels = c('Mediocre','High'))
plot(playstore$Rating, main = "Distribution of App Rating, Categorical", xlab = "Rating", ylab = "Count", col="red")

playstore$Rating = factor(playstore$Rating)
playstore <- na.omit(playstore)

```


## Training/Test Split

Inital training and test split ratio will be 70/30

```{r,echo=FALSE}

#Split into training and test set

ps_sampling <- createDataPartition(playstore$Rating, times = 1, p = 0.7, list = FALSE)

ps_training <- playstore[ps_sampling,]

ps_test <- playstore[-ps_sampling,]

#Upsample minority class
ps_training <- SMOTE(Rating ~ ., ps_training, perc.over = 200,perc.under = 150)
training_plot <- plot(ps_training$Rating, main = 'SMOTE Oversampling of Training Set', xlab = 'Rating', ylab = 'Count')
print(training_plot)
```

## Random Forest

```{r}
model1 <- randomForest(Rating ~ ., ps_training)
predict_rf <- predict(model1, ps_test)
plot(predict_rf, main = 'Random Forest Classification', xlab = 'Rating', ylab = 'Count',col = 'darkgreen')
rf_confusion_matrix <- confusionMatrix(data = predict_rf, reference = ps_test$Rating, positive = 'Mediocre')
print(rf_confusion_matrix)

```
## Naive Bayes 
```{r}
model2 <- naiveBayes(Rating ~ .,ps_training)
predict_nb <- predict(model2,ps_test)
plot(predict_nb, main = 'Naive Bayes Classification', xlab = 'Rating', ylab = 'Count',col = 'lightblue')
nb_confusion_matrix <- confusionMatrix(data = predict_nb, reference = ps_test$Rating, positive = 'Mediocre')
print(nb_confusion_matrix)

```